### 2017-08-24 sec-limitations.tex
Whitespace changes and minor edits.
Specify what exact additive constant was used for smoothing.

As is the case with traditional hidden Markov models, it is often important
to smooth the underlying model's distributions to ensure that there is a
non-zero probability of generating the observations. We employed a simple
additive smoothing in our implementation with a small additive constant for
all of our transition matrices to avoid this problem.

>>>>

As is the case with traditional hidden Markov models, it is often important
to smooth the underlying model's distributions to ensure that there is a
non-zero probability of generating the observations. We employed a simple
additive smoothing in our implementation with a small additive constant
($10^{-6}$) for all of our transition matrices to avoid this problem.
